Manuscript

### 2017-06-16 manuscript.Rmd
Added Dave Ederer as a co-author

---
title: "Manuscript"
author: "Nico Boyd, Greg Macfarlane, Kari Watkins"
date: "6/16/2017"
output:
  pdf_document: default
  html_document: default
---

>>>>

---
title: "Manuscript"
author: "Nico Boyd, Greg Macfarlane, Kari Watkins, Dave Ederer"
date: "6/16/2017"
output:
  pdf_document: default
  html_document: default
---
